Proposed Solution

### 2017-01-21 CAV17/secs/eval.tex
reorganize and add main points
remove old - add strucure

\input{table}

\begin{table*}[tpb]
\centering
\caption{Sampled configuration files for anomaly detection}
\label{table-anomaly}
\begin{footnotesize}
\begin{tabular}{|l|l|l|l|}
\hline
{\bf ID} & {\bf Problem Description} & {\bf URL} & 
{\bf \app Report}  \\ 
\hline
\hline
1 & MySQL Server has gone away error in Wamp 
& goo.gl/axnezi  
& WARNING: Violated Upper Hampel Rule for 
\\ &  & 
& {\tt max\_allowed\_packet} with value 104857600 
 \\ \hline

2 &  MySQL has abnormally high load for CPU 
& goo.gl/JrRLrR
& WARNING: Violated Upper Hampel Rule for  
\\ & & 
& {\tt sort\_buffer\_size} with value 1048576000 \\
& & & WARNING: Violated Upper Hampel Rule for  
\\ & & 
& {\tt read\_rnd\_buffer\_size} with value 283115520 \\ \hline

3 & User is having performance issues with MySQL 
& goo.gl/34jTB5
& WARNING: Violated Upper Hampel Rule for  
\\ & & 
& {\tt query\_cache\_limit} with value 134217728 \\ \hline

\end{tabular}
\end{footnotesize}
\end{table*}

\section{Evaluations}
\label{sec-eval}

We conduct three experiments to evaluate our \app
prototype. We answer the following
questions.

\begin{itemize}

\item Whether \app can successfully 
  detect real-world configuration errors ($\S$\ref{subsec-effectiveness})?

\item Whether \app can correctly detect anomalous values
($\S$\ref{subsec-anomalous})?

\item How long do training and verification last ($\S$\ref{subsec-time})?

\end{itemize}

\subsection{\app's Effectiveness}
\label{subsec-effectiveness}

We now apply \app to check against real-world misconfiguration problems.
We use a real misconfiguration dataset~\cite{configdataset}
that was collected from several online forums, \eg, 
Stack Overflow and MySQL forums.
Each configuration file in this dataset was posted by 
programmers or system administrators, 
when they confronted misconfiguration issues in practice.
This dataset contains 261 incorrect MySQL configuration files.

We apply \app to learn and check the configuration files in this
dataset. Then, we observe how many errors \app can detect.
We next manually check whether these detected errors are indeed
configuration errors.
For all the 261 configuration files, we found \app is
able to report all the errors correctly.
For 217 of the 261 configuration files, we found \app's 
error detection results are correct and accurate,
\ie, we correctly report the real misconfiguration problems
with few false positives.
For the rest of the 44 cases, 
although \app can detect the errors,
\app outputs relatively high false positives,
\eg, higher than 50 false positives,
which is not very helpful to users in practice.
The reason is our training set contains too many incorrect configuration
files, which produces a lot of noise in our learning process,
thus resulting in so many false positives.

In order to clearly evaluate the effectiveness of \app,
we extract 20 incorrect configuration files from the dataset.
\app is able to correctly report these configuration errors,
and these errors cannot be handled by any existing efforts.
Table~\ref{table-casestudy} details this information,
including the problem descriptions of these files, 
error types, and the outputs produced by \app.

As shown in Table~\ref{table-casestudy},
we found \app is capable of detecting many configuration errors previous
efforts, \eg, EnCore~\cite{zhang14encore}, cannot deal with.
To the best of our knowledge, no existing effort
is able to detect fine-grained value correlation errors in 
MySQL configuration files.
For example, the third case in Table~\ref{table-casestudy}
shows that \app can detect the following fine-grained correlation:
{\tt key\_buffer\_size} should be larger than 
{\tt thread\_size} *  {\tt sort\_buffer\_size}.

\subsection{Detecting Anomalous Values}
\label{subsec-anomalous}

The purpose of checking anomalous values in configuration files 
is to avoid potential performance or throughput problems. 
Checking anomalous values is mainly the responsibility of
the second sub-module checker of \app (see $\S$\ref{sec-checker}).

We run \app to check 30 real-world benchmarks from the Stack Overflow 
website, and found \app is able to report anomalous values in
these configurations. We also manually check whether these
anomalous values are correct by comparing our results with
answers on StackOverflow.

Table~\ref{table-anomaly} shows three examples.
We present the problem description, the link, and the output results
of \app. We found these anomalous values are very hard for
administrators or users to detect, because they look correct.
However, as shown in the links posted in Table~\ref{table-anomaly},
such anomalous values typically lead to critical performance
problems in practice.

\subsection{Training \& Verification Performance}
\label{subsec-time}

We run our experiments measuring the run-time of training and
verification of \app.
Our experiments were run on a machine equipped with
64-bit Intel Core i7-4790 CPU @ 3.60GHz and 8 GB of RAM.

\para{Training performance.}
We first evaluate the training time of \app. Namely, we examine how long
does \app need to use to generate rules.
We vary the number of configuration files in our training dataset
between 10 and 200, and record the corresponding time.
Table~\ref{table-training} presents our evaluational results.
We found the training time of \app is acceptable in practice,
because we obtained good enough rules on 150 files in the training dataset.
For 150 files, \app only requires about 7 minutes of runtime.
Furthermore, even if we train \app with a 200-file dataset,
we need less than 15 minutes, but such a training dataset
can generate about 200,000 rules.

\para{Verification performance.}
We also measure the verification time of \app, and found
that the verification time is very fast. With 232,613 rules,
\app needs less than one second to verify a MySQL configuration file.
\app only needs 3 minutes to finish the verification of 
the real-world dataset~\cite{configdataset} we used to 
evaluate the effectiveness of \app,
which contains 261 misconfiguration files.

\begin{table}[t]
\centering
\caption{Training time for different datasets}
\label{table-training}
\begin{tabular}{|c|c|}
\hline
{\bf The \# of Files for Training}       & {\bf Training Time (sec.)}  \\ 
\hline
\hline
10   & 2.997        \\ \hline
50   & 46.4208          \\ \hline
100  & 206.7798       \\ \hline
150  & 431.7772        \\ \hline
200  & 856.6383  \\ 
\hline
\end{tabular}
\end{table}

>>>>

\section{Evaluation}

\begin{table}[h]
\centering
\caption{Results of Learning}
\label{table-training}
\begin{tabular}{|c|c|c|c|}
\hline
{\bf Class of Error } & {\bf Total Rules Learned from Training Set} & {\bf Rules Detected on Benchmark set} & {\bf Thresholds}\\ 
\hline
\hline
10   & 2.997     & &  \\ \hline
50   & 46.4208   & &  \\ \hline
100  & 206.7798  & &  \\ \hline
150  & 431.7772  & &  \\ \hline
200  & 856.6383  & &  \\ 
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Training time for different datasets}
\label{table-training}
\begin{tabular}{|c|c|c|}
\hline
{\bf The \# of Files for Training} & {\bf Training Time ConfigC (sec.)} & {\bf Training Time \app (sec.)}\\ 
\hline
\hline
10   & 2.997     &   \\ \hline
50   & 46.4208   &   \\ \hline
100  & 206.7798  &   \\ \hline
150  & 431.7772  &   \\ \hline
200  & 856.6383  &   \\ 
\hline
\end{tabular}
\end{table}

### 2017-01-21 CAV17/secs/learner.tex
remove old - add strucure

The goal of the learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
In general, the learner module has two components.
The first component ($\S$\ref{subsec-rules}) 
learns rules for checking configuration errors like
missing entry errors, ordering errors, and fine-grained value correlation errors. 
These errors tend to cause total system failures, but can also be more insidious and slow down the system only when the load increase beyond a certain threshold.

Note that in \app, probabilistic typing is implemented as a learning module than can be easily extended to support more types.

>>>>

The goal of the learner is to derive rules from the intermediate representation of the training set generated by the translator.
We an interface for uses to define rules that should be learned.
Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and fine-grained value correlation errors. 
These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.

\para{Type}
In \app, probabilistic typing is implemented as an instance of the learning interface than can be easily extended to support more types. 
It

\para{Order}

\para{Missing}

\para{Integer Correlation}
Fine grained errors (Aaron)

\subsection{Checker}
\label{sec-checker}

With the learned rules and constraints in hand (generated
by the learner module),
\app checks whether any entry in a target configuration file
violates the learned rules and constraints.
For a given configuration file, \app parses it the same
way employed in the translator, thus obtaining a structured
and typed representation for the target configuration file.
Then, the checker uses two sub-modules (shown in 
Figure~\ref{fig-overview}) to check the target
configuration file based on rules and constraints.

\subsection{Implementation}

\app is primarily implemented in Haskell, with a bit of mongo.
The translator is developed as a parser for the grammar described in $\S$\ref{sec-trans}. 
The learner and checker module fully implemented the design in $\S$\ref{sec-learn} and $\S$\ref{sec-checker}, respectively.

The learning and checking modules are developed to allow
for customized extensibility. In order to verify a configuration file
against a new type of error, a user only needs to provide a new type
that is an instance of the \textit{Attribute} typeclass (\ie, define some
functions over that type). 
In particular, for each type of error the users
wish to detect, they must implement three functions;
\lstinline{learn}, \lstinline{merge}, and \lstinline{check}.

The source code for our implementation is available at {\em (URL omitted for blind review)}.
